House Price in Nanjing: Comparing Multiple Linear Regression and Random Forest

### 2023-12-01 output/paper/paper.qmd
Upload Abstract, Intro, and part of Model

---
title: "House price"
author: "Yufei Liu"
thanks: "Code and data are available at: https://github.com/Florence-Liu/house-price"
date: today
date-format: long
abstract: "."
format: pdf
number-sections: true
toc: false
bibliography: references.bib
---

@@

Gulou, Qinhuai, Xuanwu, Jianye, Qixia, Yuhuatai districts are considered as inner city while Pukou, Jiangning, Lishui, Gaochun, Liuhe districts are considered as suburban areas of Nanjing.

@@

```{r}
#| label: fig-char
#| echo: false
#| message: false
#| warning: false
#| fig-cap: Proportion of house with difference decoration status and facing south in 11 districts
#| fig-subcap: 
#|   - "South-facing"
#|   - "Decoration"
#| layout-ncol: 2

data |> group_by(District, Facing_South) |>
  summarise(n = n()) |>
  ggplot(aes(x = District, y = n, fill = factor(Facing_South))) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(y = "Number of house", fill = "Whether south-facing") +
  scale_fill_manual(values = c("#A8D8B9", "#FFD966"), labels = c("No", "Yes")) +
  theme(legend.position = "bottom", axis.text = element_text(size = 7))

data |> group_by(District, Furnished) |>
  summarise(n = n()) |>
  ggplot(aes(x = District, y = n, fill = factor(Furnished))) +
  geom_bar(stat = "identity") +
  labs(y = "Number of house", fill = "Decoration status") +
  theme_minimal() +
  scale_fill_manual(values = c("#7FCCE5", "#FF9A8B", "#A8D8B9", "#FFD966")) +
  theme(legend.position = "bottom", axis.text = element_text(size = 7))
```

@@

## Multiple Linear Regression
```{r}
#| echo: false
#| warning: false
#| message: false
#| include: false
#### Split training and testing sets ####
set.seed(777)
trainid <- sample(nrow(data), 0.8*nrow(data))
train <- data[trainid,]
test <- data[-trainid,]
```

@@

```{r}
#| label: fig-model
#| fig-cap: Variable importance of the random forest model based on MSE and Node Purity
#| echo: false
#| message: false
#| warning: false
#| layout-ncol: 2

@@

@@

district area difference, population difference, other spatial data for detailed analysis.

@@

web scrapping maximun 100 pages

>>>>

---
title: "House Price in Nanjing: Comparing Multiple Linear Regression and Random Forest"
author: "Yufei Liu"
thanks: "Code and data are available at: https://github.com/Florence-Liu/house-price"
date: today
date-format: long
abstract: "House price in Nanjing has grown rapidly and became a concern in recent years. This paper examines the relationship between house price in Nanjing, structural attributes of the property, and location using open data collected from Lianjia.com, and predict house price in Nanjing with different models. We find a geographically-imbalanced distribution of house price in Nanjing with large variance within and between each district. By comparing the MAE and RMSE, we find the random forest model gives a better prediction accuracy than the multiple linear regression model. Further work could include geocoding data to perform spatial autocorrelation analysis that consider the spatial effect in the data. "
format: pdf
number-sections: true
toc: false
bibliography: references.bib
---

@@

House prices in China has grown rapidly since 2000, and cities such as Shanghai, Beijing, and Shenzhen are among the highest around the world today [@citeHouseincrease]. Nanjing, which is located in the heart of Yangtze River Delta in eastern China and approximately 300 km from Shanghai, is the capital city for Jiangsu Province, one of the most economically developed provinces in China [@citeNanjing]. The house price in Nanjing has been a concern due to increased population in recent years [@citeConcern].

In this paper, we investigate how structural attributes and location of house affect the total house price and explore the characteristics of residential housing. We are also interested in predicting house price in Nanjing using different models. We use` Python` to collect data from Lianjia.com and `R` to clean and analyze collected data. We construct a multiple linear regression model with total house price explained by 9 other variables representing structural characteristics and location, and a random forest regression model with same variables. We find that the house price in Nanjing is geographically-imbalanced and even the variance within each district is large, indicating possible income and wealth inequality. Comparing two models with Mean Absolute Error (MAE) and Root Mean Squared Error (RMSE), we find that the random forest model gives a better prediction accuracy on both test and train data, indicating possible non-linear relationships between variables. Further work could include geospatial data to find spatial correlations and consider a more comprehensive model including more attributes such as surronding environment.

The remainder of this paper is structured as follows: @sec-data discusses the data with @sec-data_description including information about data collection and data cleaning results, and @sec-data_visualization including graphs and tables representing relationships between variables and distributions of variables; @sec-model introduces the split of train/test data and two models: a multiple linear regression model and a random forest regression model, and specifies parameters; @sec-result shows the estimates of fitted models and compares two models; @sec-discussion includes discussions about model results and implications with @sec-weakness talking about the weaknesses and future improvement.

@@

```{r}
#| label: fig-char
#| echo: false
#| message: false
#| warning: false
#| fig-cap: Proportion of house with difference decoration status and whether facing south in 11 districts
#| fig-subcap: 
#|   - "South-facing"
#|   - "Decoration"
#| layout-ncol: 2

data |> group_by(District, Facing_South) |>
  summarise(n = n()) |>
  ggplot(aes(x = District, y = n, fill = factor(Facing_South))) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(y = "Number of house", fill = "Whether south-facing") +
  scale_fill_manual(values = c("#A8D8B9", "#FFD966"), labels = c("No", "Yes")) +
  theme(legend.position = "bottom", axis.text = element_text(size = 8))

data |> group_by(District, Furnished) |>
  summarise(n = n()) |>
  ggplot(aes(x = District, y = n, fill = factor(Furnished))) +
  geom_bar(stat = "identity") +
  labs(y = "Number of house", fill = "Decoration status") +
  theme_minimal() +
  scale_fill_manual(values = c("#7FCCE5", "#FF9A8B", "#A8D8B9", "#FFD966")) +
  theme(legend.position = "bottom", axis.text = element_text(size = 8))
```

@@

We will use two machine learning algorithms in this analysis: a multiple linear regression model, and a random forest regression model. We will randomly split our data into training and testing datasets with 80% being training data and 20% being testing data.

## Multiple Linear Regression

The multiple linear regression model is shown as:

\begin{align*}
Y = \beta_{0} + \sum^{i=1}_{n} \beta_ix_i + \epsilon = \beta_0 + \beta_1x_1 + \beta_2x_2 + \cdots + \beta_nx_n + \epsilon  
\end{align*}

where

* $Y$ is the response variables `Total_Price`
* $x_i(i = 1,2,\cdots,n)$ are explanatory variables. In this case we have 9 explanatory variables
* $\beta_0$ is the intercept of the model
* $b_i(i = 1,2,\cdots,n)$ are regression coefficients
* $\epsilon$ is the random error

```{r}
#| echo: false
#| warning: false
#| message: false
#| include: false
#### Split training and testing sets ####
set.seed(777)
trainid <- sample(nrow(data), 0.8*nrow(data))
train <- data[trainid,]
test <- data[-trainid,]
```

@@

```{r}
#| label: fig-model
#| echo: false
#| message: false
#| warning: false
#| fig-cap: Variable importance of the random forest model based on MSE and Node Purity
#| fig-subcap: 
#|   - "MSE"
#|   - "Node Purity"
#| layout-ncol: 2

@@

In 2013, the Nanjing Government adjusted the boundaries and administrative divisions of Nanjing. Since then, there are 11 districts in Nanjing with Gulou, Qinhuai, Xuanwu, Jianye districts considered as inner proper while Qixia, Yuhuatai, Pukou, Jiangning, Lishui, Gaochun, Liuhe districts are considered as suburban areas of Nanjing [@citeDivision].

@@

district area difference, population difference

@@

web scrapping maximum 100 pages

Hedonic pricing model, other spatial data for detailed analysis.
